---
title: 'ASsignment2'
author: "Evan Blosser"
date: '`r format(Sys.Date(),format="%A, %B %d, %Y")`'
output: 
  html_document:
    df_print: paged
    fig_caption: true
    highlights: pygments
    number_sections: no
    theme: spacelab
    toc: yes
    toc_float: yes
---

```{r setup, include=FALSE, fig.align='center'}
knitr::opts_chunk$set(echo = TRUE)
```

# Questions{0/17}

## Q 1{.tabset}

### a
Given that an expert examining a pair of matched prints has a success rate of $92.12\%$, then that would mean that an expert will have a probability of $7.88\%$ failing to identify the match. 

### b
Given a novice with matched prints, the probability of identification failure is $25.45\%$.

### c
The participant is most likely a **novice**; that would fail to identify a match. 



## Q 2{.tabset}
```{r}
plot(1:10)
```


## Q 3{.tabset}


## Q 4{.tabset}


## Q 5{.tabset}


## Q 6{.tabset}


## Q 7{.tabset}


## Q 8{.tabset}


## Q 9{.tabset}


## Q 10{.tabset}


## Q 11{.tabset}


## Q 12{.tabset}


## Q 13{.tabset}


## Q 14{.tabset}


## Q 15{.tabset}


## Q 16{.tabset}


## Q 17{.tabset}


