---
title: 'ASsignment2'
author: "Evan Blosser"
date: '`r format(Sys.Date(),format="%A, %B %d, %Y")`'
output: 
  html_document:
    df_print: paged
    fig_caption: true
    highlights: pygments
    number_sections: no
    theme: spacelab
    toc: yes
    toc_float: yes
---

```{r setup, include=FALSE, fig.align='center'}
knitr::opts_chunk$set(echo = TRUE)
```

# Questions{2/17}

## Q 1{.tabset}

### a
Given that an expert examining a pair of matched prints has a success rate of $92.12\%$, then that would mean that an expert will have a probability of $7.88\%$ failing to identify the match. 

### b
Given a novice with matched prints, the probability of identification failure is $25.45\%$.

### c
The participant is most likely a **novice**; that would fail to identify a match. 



## Q 2{.tabset}
Given a population size of $1,000$ it is defined that $100$ of them are testesterone users, **users**, while the remainder $(900)$ are **non-users**. Within this population, $50$ **users** would test poistive while $9$ **non-users** would test negitive. 


### a
The probability that a **user** would test positive is:
$$
\begin{align*}
P(Positive|User) = 50/100 = 0.50
\end{align*}
$$

### b
The probability that a **non-user** would test positive is:
$$
\begin{align*}
P(Negative|Non-User) = (891)/900 =  0.99
\end{align*}
$$

### c
Given $P(User) = 0.10$, Baye's Rule states:
$$
\begin{align*}
P(User| Positive) = \frac{P(Positive|User)\cdot P(User)}{P(Positive|User)\cdot P(User)+ P(Positive|Non-User)\cdot P(Non-User)}
\end{align*}
$$
where:
$$
\begin{align*}
P(Positive|Non-User) = 9/900 = 0.01
\end{align*}
$$
it can then be Obtained that:
$$
\begin{align*}
P(User| Positive)= \frac{(0.1)\cdot(0.5)}{(0.1)\cdot(0.5)+(0.9)\cdot(0.01)} = 0.8474576
\end{align*}
$$
or The probability that a Player that tests **positive** is infact a **user** is $\approx 84.75\%$.


## Q 3{.tabset}

### Theorem 3.1
"The Multiplicative Rule 
You have *k* sets of elements; $n_1$ for the first set, $n_2$ for the second set..., and $n_k$ for the $k^{th}$ set. Suppose you want to form a sample of *k* elements by taking one element from each of the *k* sets. The number of different samples that can be formed is the product":
$$
\begin{align*}
n_1n_2n_3&...n_k\\
o&r\\ 
\prod_{i = 1}^{k}& n_{i}
\end{align*}
$$

### Proof
The book builds a proof for $n_1n_2$ using pairings of $a_{n1}b_{n2}$ and a $2D$ Table to represent the possibilities. In order to prove this for *k* sets the proof must be elaborated upon:
$$
\begin{align*}
\begin{bmatrix}
    & b_1 & b_2 & ...   & b_{n2}\\
a_1 & a_1b_1 & a_1b_2& ... & a_1b_{n2}  \\
a_2 & a_2b_1 & a_2b_2&...  &...   \\
... & ...    & ...& ...&    ...    \\
a_{n1}&a_{n1}b_1&...&...&a_{n1}b_{n2}
\end{bmatrix} \cdot 
\begin{bmatrix}
    & d_1 & d_2 & ...   & d_{nk}\\
c_1 & c_1d_1 & c_1d_2& ... & c_1d_{nk}  \\
c_2 & c_2d_1 & c_2d_2&...  &...   \\
... & ...    & ...& ...&    ...    \\
c_{n3}&c_{n3}d_1&...&...&c_{n3}d_{nk}
\end{bmatrix}  
\end{align*}
$$
These tables ellaborate on the books proof of $(n_1n_2)n_3=n_1n_2n_3$ to state that:
$$
\begin{align*}
(n_1n_2n_3)...n_k = n_1n_2n_3...n_k 
\end{align*}
$$

## Q 4{.tabset}

### Theorem 3.2
"Permutations Rule Given a single set of **N** distinctly different elements, you wish to select *n* elements from the **N** and  arrange them within *n* positions in a distinct order. The number of different permutations of the **N** elements taken *n* at a time is denoted buy $P^N_n$ and is equal to": 
$$
\begin{align*}
P^N_n  = N(N-1)(N-2)...(N-n+1) = \frac{N!}{(N-n)!}
\end{align*}
$$

### Proof
Given, $P^N_n$, is *n* elements within **N**, and arranged in *n* positions. The total amount of distinct ways this will be able to happen first is **N** ways. Thus , we find the first position, of *n* positions, to be **N**, or:
$$
\begin{align*}
P^N_n  = (N)...
\end{align*}
$$

each subsequent position has 1 less then **N** amount of possible or distinct elements *n* to be chosen, thus if we want to fill the second position we have $N-1$ distinct elements that can be chosen. This follows for each one chosen as we work **withouth replacement**, thus the third position and subsequent positions to be filled will follows as $(N-2)(N-3)...$ such that:
$$
\begin{align*}
P^N_n  = N(N-1)(N-2)...
\end{align*}
$$
Here we must note that a $0$ trial is not desired and given the correct count, it can be determined that the last position can be filled by $(N-n+1)$ distinct ways, such that if $N=n$ then there is at minimum 1 distinct way:
$$
\begin{align*}
P^N_n  = N(N-1)(N-2)...(N-n+1) = \frac{N!}{(N-n)!}
\end{align*}
$$



## Q 5{.tabset}

### Theorem 3.3

### Proof


## Q 6{.tabset}

### Theorem 3.4

### Proof



## Q 7{.tabset}


## Q 8{.tabset}


## Q 9{.tabset}


## Q 10{.tabset}


## Q 11{.tabset}


## Q 12{.tabset}


## Q 13{.tabset}


## Q 14{.tabset}


## Q 15{.tabset}


## Q 16{.tabset}


## Q 17{.tabset}

```{r}
plot(1:10)
```
