---
title: 'ASsignment2'
author: "Evan Blosser"
date: '`r format(Sys.Date(),format="%A, %B %d, %Y")`'
output: 
  html_document:
    df_print: paged
    fig_caption: true
    highlights: pygments
    number_sections: no
    theme: spacelab
    toc: yes
    toc_float: yes
---

```{r setup, include=FALSE, fig.align='center'}
knitr::opts_chunk$set(echo = TRUE)
```

# Questions{2/17}

## Q 1{.tabset}

### a
Given that an expert examining a pair of matched prints has a success rate of $92.12\%$, then that would mean that an expert will have a probability of $7.88\%$ failing to identify the match. 

### b
Given a novice with matched prints, the probability of identification failure is $25.45\%$.

### c
The participant is most likely a **novice**; that would fail to identify a match. 



## Q 2{.tabset}
Given a population size of $1,000$ it is defined that $100$ of them are testesterone users, **users**, while the remainder $(900)$ are **non-users**. Within this population, $50$ **users** would test poistive while $9$ **non-users** would test negitive. 


### a
The probability that a **user** would test positive is:
$$
\begin{align*}
P(Positive|User) = 50/100 = 0.50
\end{align*}
$$

### b
The probability that a **non-user** would test positive is:
$$
\begin{align*}
P(Negative|Non-User) = (891)/900 =  0.99
\end{align*}
$$

### c
Given $P(User) = 0.10$, Baye's Rule states:
$$
\begin{align*}
P(User| Positive) = \frac{P(Positive|User)\cdot P(User)}{P(Positive|User)\cdot P(User)+ P(Positive|Non-User)\cdot P(Non-User)}
\end{align*}
$$
where:
$$
\begin{align*}
P(Positive|Non-User) = 9/900 = 0.01
\end{align*}
$$
it can then be Obtained that:
$$
\begin{align*}
P(User| Positive)= \frac{(0.1)\cdot(0.5)}{(0.1)\cdot(0.5)+(0.9)\cdot(0.01)} = 0.8474576
\end{align*}
$$
or The probability that a Player that tests **positive** is infact a **user** is $\approx 84.75\%$.


## Q 3{.tabset}

### Theorem 3.1

### Proof



## Q 4{.tabset}

### Theorem 3.2

### Proof




## Q 5{.tabset}

### Theorem 3.3

### Proof


## Q 6{.tabset}

### Theorem 3.4

### Proof



## Q 7{.tabset}


## Q 8{.tabset}


## Q 9{.tabset}


## Q 10{.tabset}


## Q 11{.tabset}


## Q 12{.tabset}


## Q 13{.tabset}


## Q 14{.tabset}


## Q 15{.tabset}


## Q 16{.tabset}


## Q 17{.tabset}

```{r}
plot(1:10)
```
