---
title: 'ASsignment2'
author: "Evan Blosser"
date: '`r format(Sys.Date(),format="%A, %B %d, %Y")`'
output: 
  html_document:
    df_print: paged
    fig_caption: true
    highlights: pygments
    number_sections: no
    theme: spacelab
    toc: yes
    toc_float: yes
---

```{r setup, include=FALSE, fig.align='center'}
knitr::opts_chunk$set(echo = TRUE)
```

# Questions{2/17}

## Q 1{.tabset}

### a
Given that an expert examining a pair of matched prints has a success rate of $92.12\%$, then that would mean that an expert will have a probability of $7.88\%$ failing to identify the match. 

### b
Given a novice with matched prints, the probability of identification failure is $25.45\%$.

### c
The participant is most likely a **novice**; that would fail to identify a match. 



## Q 2{.tabset}
Given a population size of $1,000$ it is defined that $100$ of them are testesterone users, **users**, while the remainder $(900)$ are **non-users**. Within this population, $50$ **users** would test poistive while $9$ **non-users** would test negitive. 


### a
The probability that a **user** would test positive is:
$$
\begin{align*}
P(Positive|User) = 50/100 = 0.50
\end{align*}
$$

### b
The probability that a **non-user** would test positive is:
$$
\begin{align*}
P(Negative|Non-User) = (891)/900 =  0.99
\end{align*}
$$

### c
Given $P(User) = 0.10$, Baye's Rule states:
$$
\begin{align*}
P(User| Positive) = \frac{P(Positive|User)\cdot P(User)}{P(Positive|User)\cdot P(User)+ P(Positive|Non-User)\cdot P(Non-User)}
\end{align*}
$$
where:
$$
\begin{align*}
P(Positive|Non-User) = 9/900 = 0.01
\end{align*}
$$
it can then be Obtained that:
$$
\begin{align*}
P(User| Positive)= \frac{(0.1)\cdot(0.5)}{(0.1)\cdot(0.5)+(0.9)\cdot(0.01)} = 0.8474576
\end{align*}
$$
or The probability that a Player that tests **positive** is infact a **user** is $\approx 84.75\%$.


## Q 3{.tabset}

### Theorem 3.1
"The Multiplicative Rule 
You have *k* sets of elements; $n_1$ for the first set, $n_2$ for the second set..., and $n_k$ for the $k^{th}$ set. Suppose you want to form a sample of *k* elements by taking one element from each of the *k* sets. The number of different samples that can be formed is the product":
$$
\begin{align*}
n_1n_2n_3&...n_k\\
o&r\\ 
\prod_{i = 1}^{k}& n_{i}
\end{align*}
$$

### Proof
The book builds a proof for $n_1n_2$ using pairings of $a_{n1}b_{n2}$ and a $2D$ Table to represent the possibilities. In order to prove this for *k* sets the proof must be elaborated upon:
$$
\begin{align*}
\begin{bmatrix}
    & b_1 & b_2 & ...   & b_{n2}\\
a_1 & a_1b_1 & a_1b_2& ... & a_1b_{n2}  \\
a_2 & a_2b_1 & a_2b_2&...  &...   \\
... & ...    & ...& ...&    ...    \\
a_{n1}&a_{n1}b_1&...&...&a_{n1}b_{n2}
\end{bmatrix} \cdot 
\begin{bmatrix}
    & d_1 & d_2 & ...   & d_{nk}\\
c_1 & c_1d_1 & c_1d_2& ... & c_1d_{nk}  \\
c_2 & c_2d_1 & c_2d_2&...  &...   \\
... & ...    & ...& ...&    ...    \\
c_{n3}&c_{n3}d_1&...&...&c_{n3}d_{nk}
\end{bmatrix}  
\end{align*}
$$
These tables ellaborate on the books proof of $(n_1n_2)n_3=n_1n_2n_3$ to state that:
$$
\begin{align*}
(n_1n_2n_3)...n_k = n_1n_2n_3...n_k 
\end{align*}
$$

## Q 4{.tabset}

### Theorem 3.2
"Permutations Rule Given a single set of **N** distinctly different elements, you wish to select *n* elements from the **N** and  arrange them within *n* positions in a distinct order. The number of different permutations of the **N** elements taken *n* at a time is denoted buy $P^N_n$ and is equal to": 
$$
\begin{align*}
P^N_n  = N(N-1)(N-2)...(N-n+1) = \frac{N!}{(N-n)!}
\end{align*}
$$

### Proof
Given, $P^N_n$, is *n* elements within **N**, and arranged in *n* positions. The total amount of distinct ways this will be able to happen first is **N** ways. Thus , we find the first position, of *n* positions, to be **N**, or:
$$
\begin{align*}
P^N_n  = (N)...
\end{align*}
$$

each subsequent position has 1 less then **N** amount of possible or distinct elements *n* to be chosen, thus if we want to fill the second position we have $N-1$ distinct elements that can be chosen. This follows for each one chosen as we work **withouth replacement**, thus the third position and subsequent positions to be filled will follows as $(N-2)(N-3)...$ such that:
$$
\begin{align*}
P^N_n  = N(N-1)(N-2)...
\end{align*}
$$
Here we must note that a $0$ trial is not desired and given the correct count, it can be determined that the last position can be filled by $(N-n+1)$ distinct ways, such that if $N=n$ then there is at minimum 1 distinct way:
$$
\begin{align*}
P^N_n  = N(N-1)(N-2)...(N-n+1)
\end{align*}
$$
Next we Use the **multiplicitivce rule** as follows, where $n! = n \times (n-1)!$:
$$
\begin{align*}
P^N_n  =& N(N-1)(N-2)...(N-n+1) \cdot \frac{(N-n)!}{(N-n)!}\\
       =& \frac{N(N-1)(N-2)...(N-n+1) \cdot(N-n)!}{(N-n)!}\\
       =&  \frac{N!}{(N-n)!}
\end{align*}
$$
Thus:
$$
\begin{align*}
P^N_n  =  \frac{N!}{(N-n)!}
\end{align*}
$$

## Q 5{.tabset}

### Theorem 3.3
Partitions Rule: There exsists a single set of **N** distinctly diffrent elements and you want to partition them into *k* sets, the first set contianing $n_1$ elements, the second containt $n_2$ elemetns ... and the $k^{th}$ set containing $n_k$ elements. The number of different partitions is:
$$
\begin{align*}
A = \frac{N!}{n_1!n_2!...n_k!}\hspace{10mm} \textit{where:}\hspace{5mm} n_1+n_2+...+n_k = N 
\end{align*}
$$



### Proof
By the use of **Theorem 3.2** we can say that:
$$
\begin{align*}
P^N_N = \frac{N!}{(N-N)!} = \frac{N!}{0} = N!
\end{align*}
$$
Next by using **Theorem 3.1** 
$$
\begin{align*}
P^N_N = N! = (A)(n_1!)(n_2!)...(n_k!)
\end{align*}
$$
Thus:
$$
\begin{align*}
\frac{N!}{(n_1!)(n_2!)...(n_k!)} = (A)
\end{align*}
$$

## Q 6{.tabset}



### Theorem 3.4
The Combinations Rule: A sample of *n* elements is to be chosen from a set of **N** elements. Then the number opf different samples of *n* elements that can be selected from **N** is denoted by 
$$
\begin{pmatrix} 
N\\
n
\end{pmatrix}
$$
and is equal to:
$$
\begin{pmatrix} 
N\\
n
\end{pmatrix} = \frac{N!}{n!(N-n)!}
$$

### Proof



## Q 7{.tabset}

### a
The probabilities for *y* in the table does sum to equal 1
```{r}
0.09+0.30+0.37+0.20+.04
```


### b
The probability of 3 or 4 homes, $P(3\cup4)P(y=3)+P(y=4)$, is $0.24$. 
```{r}
.2+0.04
```


### c
The probability of fewer thena 2 homes, $P(y<2) = P(y=0)+P(y=1)$, is $0.39$
```{r}
0.3+.09
```



## Q 8{.tabset}

### a
Checking that this is a discrete random variable distribution, or the summation of the probabilities is 1, we fins that it does satisfy the properties:
```{r}
.17+.1+.11+.11+.1+.1+.07+.05+.03+.02+.02+.02+.02+.02+.01+.01+.01+.01+.01+.005+.005
```


### b
For the probability $P(Y\geq10)$ it can be seen that the probability is $0.14$:
```{r}
Q8.B.prob<- c(.17, .1,.11,.11,.1,.1,.07,.05,.03,.02,.02,.02,.02,.02,.01,.01,.01,.01,.01,.005,.005)
Q8.B.num <- c(0:20)
Q8.B.tab <- data.frame(Q8.B.num,Q8.B.prob)
Q8.B.tab
```


```{r}
Q8.B.tab.answer <- Q8.B.tab[11:21,]
sum(Q8.B.tab.answer)
```


### c
The mean is, $\mu = E(Y)=\sum y\cdot p(y) = 4.655$:
```{r}
0*.17+1*.1+2*.11+3*.11+4*.1+5*.1+6*.07+7*.05+8*.03+9*.02+10*.02+11*.02+12*.02+13*.02+14*.01+15*.01+16*.01+17*.01+18*.01+19*.005+20*.005
```
The variance is, $\sigma^2 = V(Y)=\sum y^2\cdot p(y) - \mu^2 = 19.85597$
```{r}
0^2*.17+1^2*.1+2^2*.11+3^2*.11+4^2*.1+5^2*.1+6^2*.07+7^2*.05+8^2*.03+9^2*.02+10^2*.02+11^2*.02+12^2*.02+13^2*.02+14^2*.01+15^2*.01+16^2*.01+17^2*.01+18^2*.01+19^2*.005+20^2*.005 - 4.655^2
```


### d
The interval from Chebyshev's Rule can be used for $\frac{3}{4}$ or $0.75$ probability; which states $(\mu \pm 2\sigma)$. Thus the interval is:
$$
(-4.257008,13.56701)
$$



```{r}
4.655 - 2*sqrt(19.85597)
4.655 + 2*sqrt(19.85597)
```



## Q 9{.tabset}

### a


### b


### c


### d



## Q 10{.tabset}


## Q 11{.tabset}


## Q 12{.tabset}


## Q 13{.tabset}


## Q 14{.tabset}


## Q 15{.tabset}


## Q 16{.tabset}


## Q 17{.tabset}


